Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-05-09 Paper.tex
before table experiments

In a survey of optimization techniques being used within operations management, the authors have broken the realm into three distinct sectors. These can be identified as input management, facilities management, and output management. Stated more simply, these correspond to scheduling, production, and vehicle routing. Failure to optimize any one of these areas can lead large inefficiencies (i.e. lost revenue) for a company. Making too much of one product leads to inventory costs, failure to plan good routes leads to higher shipping costs, and not spending enough on advertising leads to missed opportunities and subpar performance. Johnannesson and Karsten go on to say, ``As such problems often have a large scale, the impact can be significant. For example, it is not uncommon to be able to decrease logistics spending by 5 to 10 percent in a supply chain with annual logistics costs of over \$100 million. 

@@

while they concluded that many operations management/production problems can be solved using linear programming, it may not always be the best approach.  However, by adjusting settings and parameters in software-based solvers, many large-scale problems can be effectively solved in this way.\cite{klotz}  This Golf-Sport problem falls squarely within the facilities management/production sector.  Fei et al discovered that for large-scale production optimizations, heuristics were necessarily utilized.  Additionally, the most common solution approaches utilize branch-and-cut or branch-and-price.\cite{survey}

@@

Golf-Sport is a small-sized company that produces high-quality components for people who build their own golf clubs and prebuilt sets of clubs. There are five components:  steel shafts, graphite shafts, forged iron heads, metal wood heads, and metal wood heads with titanium inserts; these products are produced in three plants:  Chandler, Glendale, and Tucson. Each plant can produce any of the components, although each plant has a different set of individual constraints and unit costs. These constraints cover labor and packaging machine time (the machine is used by all components). Note that even though the components are identical in the three plants, different production processes are used, and therefore the products use different amounts of resources in different plants.

@@

The solution will presented as three options for production and sales: (1) manufactured and sold in month one; (2) manufactured and sold in month two; and (3) manufactured in month one and sold in month two. In this problem, two types of constraints exist: local and global. This two-month optimization can serve as a baseline and could later be expanded to more periods if desired. This particular problem appears to lend itself to integer programming as the ideal optimization method. The problem will be coded and solved using MATLAB's optimization toolbox functionality.

@@

\subsection{Objective}
The objective of this model is to maximize profit, represented as the difference between sales revenue and cost.  For the purposes of this function let \textit{R, C} \& \textit{I} represent revenue, product cost, and inventory cost, respectively.  The function can be expressed as:
%align functions to the left

@@

The total revenue from all products produced and sold, less the cost of manufacture and inventory, is represented in this function.  While designed for a two-period optimization, the base function can be easily expanded to accomodate for more periods of production and sales.
%superscript for plant, sub for product and period??
\subsection{Constraints}
In construction of this model, the following constraints were constructed within the parameters set forth by the problem:
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq L_{1} %Labor
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq L_{2} % Labor
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq P_{1} %packing
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq P_{2}%packing
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq A %advertise
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq A %advertise
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} + e \leq G_{1},  i = g, y, z %graphite
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq G_{2} + e, i = g, y, z %graphite
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq U_{1} , i = v, u, y, z %set assembly
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq U_{2},  i = v, u, y, z %set assembly
\end{equation}
\begin{equation}
Min_{1} \leq x_{i,1} \leq Max_{1} %What is a good variable for the constants for sales bounds
\end{equation}
\begin{equation}
Min_{2} \leq x_{i,2} + x_{i,3} \leq Max_{2}
\end{equation}
\begin{equation}
x_{i,j} \geq 0, integer %how to best put this into math speak
\end{equation}
\begin{equation}
e \geq 0
\end{equation}

@@

\section{Solution}
The model was successfully optimized to the same solution over several runs, yielding the following optimal solution with constraints as laid out in the original problem above:
\\
\\
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Chandler Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 251 \\
Graphite Shafts & 100 & 2000 & 0 \\
Iron Heads & 200 & 0 & 200 \\
Metal Wood Heads & 35 & 1 & 30 \\
Titanium Insert Wood Heads & 2000 & 1299 & 701 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 35 & 84\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Glendale Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 0 \\
Graphite Shafts & 100 & 100 & 0 \\
Iron Heads & 200 & 199 & 1 \\
Metal Wood Heads & 36 & 30 & 6 \\
Titanium Insert Wood Heads & 2000 & 1289 & 711 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 68 & 83\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l c c c }
\hline
\multicolumn{4}{|c|}{Optimal Tucson Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 1 & 0 & 2 \\
Graphite Shafts & 431 & 1265 & 2 \\
Iron Heads & 100 & 0 & 100 \\
Metal Wood Heads & 339 & 0 & 139 \\
Titanium Insert Wood Heads & 2000 & 814 & 1186 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 92 & 92\\
\end{tabular}
%end{table} dont remove
\\
\\
\vspace{5mm}
\\

@@

\begin{tabular}{ l c c c }

>>>>

In a survey of optimization techniques being used within operations management, the authors have broken the realm into three distinct sectors. These can be identified as input management, facilities management, and output management. Stated more simply, these correspond to scheduling, production, and vehicle routing, respectively. Failure to optimize any one of these areas can to lead large inefficiencies (i.e. lost revenue) for a company. Making too much of one product leads to inventory costs, failure to plan good routes leads to higher shipping costs, and not spending enough on advertising leads to missed opportunities and subpar performance. Johnannesson and Karsten go on to say, ``As such problems often have a large scale, the impact can be significant. For example, it is not uncommon to be able to decrease logistics spending by 5 to 10 percent in a supply chain with annual logistics costs of over \$100 million. 

@@

while they concluded that many operations management/production problems can be solved using linear programming, it may not always be the best approach.  However, by adjusting settings and parameters in software-based solvers, many large-scale problems can be effectively solved in this way.\cite{klotz}  This Golf-Sport problem falls squarely within the facilities management/production sector.  Fei et al. discovered that for large-scale production optimizations, heuristics were necessarily utilized.  Additionally, the most common solution approaches utilize branch-and-cut or branch-and-price.\cite{survey}

@@

Golf-Sport is a small-sized company that produces high-quality components for people who build their own golf clubs and prebuilt sets of clubs. There are five components:  steel shafts, graphite shafts, forged iron heads, metal wood heads, and metal wood heads with titanium inserts; these products are produced in three plants:  Chandler, Glendale, and Tucson. Each plant can produce any of the components, although each plant has a different set of individual constraints and unit costs. These constraints cover labor and packaging machine time (the machine is used for all components). Note that even though the components are identical in the three plants, different production processes are used, and therefore the products use different amounts of resources in different plants.

@@

The solution will presented as items produced and sold according to the following method: (1) manufactured and sold in month one; (2) manufactured and sold in month two; and (3) manufactured in month one and sold in month two. In this problem, two types of constraints exist: local and global. This two-month optimization can serve as a baseline and could later be expanded to more periods if desired. This particular problem appears to lend itself to integer programming as the ideal optimization method. The problem will be coded and solved using MATLAB's optimization toolbox functionality.

@@

\subsection{Objective}
The objective of this model is to maximize profit, represented as the difference between sales revenue and cost.  For the purposes of this function let \textit{R, C,} and \textit{I} represent revenue, product cost, and inventory cost, respectively.  The function can be expressed as:
%align functions to the left

@@

The total revenue from all products produced and sold, minus the cost of manufacture and inventory, is represented in this function.  While designed for a two-period optimization, the base function can be easily expanded to accomodate for more periods of production and sales.
%superscript for plant, sub for product and period??
\subsection{Constraints}
In construction of this model, the following constraints were constructed within the parameters set forth by the problem:
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq L_{1} %Labor
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq L_{2} % Labor
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq P_{1} %packing
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq P_{2}%packing
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq A %advertise
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq A %advertise
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} + e \leq G_{1},  i = g, y, z %graphite
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq G_{2} + e, i = g, y, z %graphite
\end{equation}
\begin{equation}
\sum c_{i}x_{i,1} + \sum c_{i}x_{i,3} \leq U_{1} , i = v, u, y, z %set assembly
\end{equation}
\begin{equation}
\sum c_{i}x_{i,2} \leq U_{2},  i = v, u, y, z %set assembly
\end{equation}
\begin{equation}
Min_{1} \leq x_{i,1} \leq Max_{1} %What is a good variable for the constants for sales bounds
\end{equation}
\begin{equation}
Min_{2} \leq x_{i,2} + x_{i,3} \leq Max_{2}
\end{equation}
\begin{equation}
x_{i,j} \geq 0, integer %how to best put this into math speak
\end{equation}
\begin{equation}
e \geq 0
\end{equation}

@@

\section{Solution}
The model was successfully optimized to the same solution over several runs, yielding the following optimal solution with constraints as laid out in the original problem above:
\\
\\
\\
\noindent
%begin{table}
\begin{tabular}{ l | c | c |c }
\hline
\multicolumn{4}{|c|}{Optimal Chandler Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 251 \\
Graphite Shafts & 100 & 2000 & 0 \\
Iron Heads & 200 & 0 & 200 \\
Metal Wood Heads & 35 & 1 & 30 \\
Titanium Insert Wood Heads & 2000 & 1299 & 701 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 35 & 84\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l | c | c | c }
\hline
\multicolumn{4}{|c|}{Optimal Glendale Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 0 & 0 & 0 \\
Graphite Shafts & 100 & 100 & 0 \\
Iron Heads & 200 & 199 & 1 \\
Metal Wood Heads & 36 & 30 & 6 \\
Titanium Insert Wood Heads & 2000 & 1289 & 711 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 68 & 83\\
\end{tabular}
%end{table} dont remove
\vspace{5mm}
\\
\noindent
%begin{table}
\begin{tabular}{ l | c | c | c }
\hline
\multicolumn{4}{|c|}{Optimal Tucson Production} \\
\hline
\textbf{Item} & \textbf{Period 1} & \textbf{Period 2} & \textbf{Period 1 Carryover} \\
Steel Shafts & 1 & 0 & 2 \\
Graphite Shafts & 431 & 1265 & 2 \\
Iron Heads & 100 & 0 & 100 \\
Metal Wood Heads & 339 & 0 & 139 \\
Titanium Insert Wood Heads & 2000 & 814 & 1186 \\
Set, Steel, Metal Heads & 0 & 0 & 0 \\
Set, Steel, Titanium Heads & 0 & 0 & 0 \\
Set, Graphite, Metal Heads & 0 & 0 & 0 \\
Set, Graphite, Titanium Heads & 0 & 92 & 92\\
\end{tabular}
%end{table} dont remove
\\
\\
\vspace{5mm}
\\

@@

\begin{tabular}{ l | c | c | c }
